Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-19 prop_iop.tex
prop_iop.tex Updating here and there, and found the previous footnote is wrong... orz

\begin{example}[Three-dimensional quantum three-interval-valued probability
measure]\label{ex:three-dimensional-three-value} Given a three dimensional
Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Let $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $, $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and 
\begin{equation}\eqalign{ 
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})=\imposs\textrm{ ,}\\ 
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\textrm{ ,}\\ 
\bar{\mu}(P) = \unknown\qquad\textrm{otherwise.} 
}\end{equation}
It is straightforward to verify that $\bar{\mu}$ is a convex quantum
interval-valued probability measure. Now assume there exists a real-valued
quantum probability measure $\mu$ such that $\mu(P)\in\bar{\mu}(P)$
for every event (projection)~$P$. We derive a contradiction as follows.
Suppose $\mu(P)\in\bar{\mu}(P)$ then we must have $\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0$.
By Gleason's theorem, there is a mixed state~$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$
such that $\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. However, no pure state~$\ket{\phi}$
can satisfy $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$; a contradiction.
\end{example}

@@

\begin{lemma}\label{lemma:interval-valued-frame-function}An interval-valued
frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$ satisfies
the following properties:
\begin{itemize}
\item $\bar{f}\left(\lambda\ket{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
for any $\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$,
we have $1\in\sum_{i=0}^{2}\bar{f}\left(\ket{\psi_{i}}\right)$ and
$\left[1,1\right]-\bar{f}\left(\ket{\psi_{i}}\right)\subseteq\bar{f}\left(\ket{\psi_{j}}\right)+\bar{f}\left(\ket{\psi_{k}}\right)$,
where $i$, $j$, and $k$ are any permutations among $0$, $1$,
and $2$.
\end{itemize}
Conversely, if a function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the above properties, $\bar{f}$ must be an interval-valued
frame function.\end{lemma}
\begin{proof}
Given a quantum IVPM~$\bar{\mu}$, it is straightforward to verify
that its interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the above properties.

Conversely, given a function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfying the above properties, consider $\bar{\mu}:\events\rightarrow\mathscr{I}$
defined by
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$ and $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
\item For any $\ket{\psi}\in\mathbb{C}S^{2}$, we have $\bar{\mu}\left(\proj{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
and $\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\left[1,1\right]-\bar{f}\left(\ket{\psi}\right)$.
\end{itemize}
Since other conditions are trivial, we only need to verify 
\begin{equation}
\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\label{eq:quantumIVPMconditions}
\end{equation}
 for any set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$.
First, if $\mathbb{0}$ or $\mathbb{1}$ is in $\left\{ P_{i}\right\} _{i=1}^{N}$,
the statement could be reduced to the case without $\mathbb{0}$,
or its trivial. Hence, we only need to discuss $\left\{ P_{i}\right\} _{i=1}^{N}$
containing 1- or 2-dimensional projectors. When $\left\{ P_{i}\right\} _{i=1}^{N}$
containing a 2-dimensional projector, the definition of $\bar{\mu}$
implies equation~(\ref{eq:quantumIVPMconditions}). When $\left\{ P_{i}\right\} _{i=1}^{N}$
only containing 1-dimensional projectors, the properties of $\bar{f}$
implies equation~(\ref{eq:quantumIVPMconditions}).
\end{proof}
\begin{definition}For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\left(\begin{array}{c}\alpha_{0}\\
\alpha_{1}\\
\alpha_{2}
\end{array}\right)$ and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}+\beta_{2}\ket{2}=\left(\begin{array}{c}\beta_{0}\\
\beta_{1}\\
\beta_{2}
\end{array}\right)$, their cross product is defined as follow: 
\begin{equation}
\ket{\psi\times\phi}=\ket{\psi}\times\ket{\phi}=\left|\begin{array}{cc}\alpha_{1}^{*} & \beta_{1}^{*}\\
\alpha_{2}^{*} & \beta_{2}^{*}
\end{array}\right|\ket{0}+\left|\begin{array}{cc}\alpha_{2}^{*} & \beta_{2}^{*}\\
\alpha_{0}^{*} & \beta_{0}^{*}
\end{array}\right|\ket{1}+\left|\begin{array}{cc}\alpha_{0}^{*} & \beta_{0}^{*}\\
\alpha_{1}^{*} & \beta_{1}^{*}
\end{array}\right|\ket{2}\textrm{ ,}
\end{equation}
where $\left|\begin{array}{cc}\alpha & \beta\\
\alpha' & \beta'
\end{array}\right|=\alpha\beta'-\alpha'\beta$. Also, even if $\ket{\psi}$ and $\ket{\phi}$ are normalized, their
cross product~$\ket{\psi}\times\ket{\phi}$ need not be normalized
as usual. We will use $\ket{\psi}\times\ket{\phi}$ and
$\ket{\psi}\times\ket{\phi}/\left\Vert
\ket{\psi}\times\ket{\phi}\right\Vert$ interchanged when there is no
confusion.\end{definition}

@@

In order to simplify the discussion, we call a function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$
satisfying conditions in lemma~\ref{lemma:interval-valued-frame-function}
a real interval-valued frame function. Obviously, any results in appendix~\ref{sec:Interval-valued-Frame-Functions}
still hold if we replace every ``complex'' by ``real,'' in particular,
replace every $\mathbb{C}S^{2}$ by $S^{2}$. Furthermore, since restricting
the domain of a complex interval-valued frame function to $S^{2}$
gives a real interval-valued frame function, if we prove there is
no real interval-valued frame function satisfying a condition, then
there must be no complex interval-valued frame function satisfying
the corresponding condition. From now on, when we write an interval-valued
frame function~$\bar{f}$ without other specification, we would always
means a real interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$.

@@

\begin{lemma}\label{lemma:imposs-imply-same-value}Given $\theta_{0}\in\left[0,\pi / 2\right]$
and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
then there is $l_{0}\in\left[0,\frac{1}{2}\right]$ such that $\bar{f}\left(\ket{\psi_{0}}\right)=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$
for any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\pi / 2-\theta_{0},\pi / 2\right]\right)$.\end{lemma}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{figureb1.eps} 
\par\end{centering}
\caption{\label{fig:three-dimensional-real-frame-1}This figure is used in
the proof of lemma~\ref{lemma:imposs-imply-same-value}.}
\end{figure}
\begin{proof}
We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-1}.
Let the yellow circle is the states whose latitude is $\theta_{0}$.
Then, every states above the yellow circle maps to $\imposs$ by $\bar{f}$.
In particular, $\bar{f}\left(\ket{0}\right)=\bar{f}\left(\ket{0'}\right)=\imposs$.
Since $\left\{ \ket{0'},\ket{1},\ket{2'}\right\} $ is an orthonormal
basis, by lemma~\ref{lemma:interval-valued-frame-function}, we have
\begin{equation}
\eqalign{\left[1,1\right]-\bar{f}\left(\ket{1}\right)\subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{2}\right)=\bar{f}\left(\ket{2'}\right)\\
\left[1,1\right]-\bar{f}\left(\ket{2'}\right)\subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{1}\right)
}
\label{eq:includes}
\end{equation}
so that $\bar{f}\left(\ket{2'}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)$.
By the same reason, for any state~$\ket{\psi}$ in the dotted black
circle between $\ket{2'}$ and $\ket{2}$, we have $\bar{f}\left(\ket{\psi}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{2'}\right)$.
Since the angle between $\ket{0}$ and $\ket{0'}$ is the same as
the angle between $\ket{2}$ and $\ket{2'}$, for any $\ket{\psi_{0}}$
and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are in the same longitude,
then $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)$.

@@

Since $\left\{ \ket{A},\ket{B},\ket{C}\right\} $ is an orthonormal
basis and $\bar{f}\left(\ket{A}\right)=\bar{f}\left(\ket{B}\right)=\bar{f}\left(\ket{C}\right)=\left[l_{0},1-l_{0}\right]$,
we have the following inequalities by
lemma~\ref{lemma:interval-valued-frame-function},
\begin{equation}\eqalign{
1\in\left[3l_{0},3-3l_{0}\right] \Rightarrow l_{0}\le\frac{1}{3}\textrm{ ,}\\
\left[1,1\right]-\left[l_{0},1-l_{0}\right]\subseteq\left[2l_{0},2-2l_{0}\right]
\Rightarrow l_{0}\le0\textrm{ .}
}\end{equation}
Recall that $0\le l_{0}\le\frac{1}{2}$. Therefore, $l_{0}=0$, that
is, $\unknown=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$.
\end{proof}

@@

\begin{example}[Three-dimensional quantum 5-interval-valued probability
measure]\label{ex:three-dimensional-5-value} Given a three dimensional
Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Let\emph{ }$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\minus}=\left(\ket{0}-\ket{1}\right)/\sqrt{2}$,
and $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess,\midd\right\} $,
where $\midd$ represents $\left[\frac{1}{4},\frac{3}{4}\right]$.
The definition of $\bar{\mu}$ below refers to figure~\ref{fig:three-dimensional-5-value}
which plots the 1-dimensional projectors: 
\begin{enumerate}
\item Let: 
\begin{equation}\eqalign{ 
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs\textrm{ ,}\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess\textrm{ ,} 
}\end{equation}
where $\ket{0}$ and $\ket{\ps}$ are plotted as the red and green
dotted vectors, respectively. 
\item The red and green circles are are the states orthogonal to $\ket{0}$
and $\ket{\ps}$, respectively. We define 
\begin{equation}\eqalign{ 
\bar{\mu}\left(\proj{\psi}\right)=\likely\textrm{ ,}\\ 
\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\unlikely\textrm{ ,} 
}\end{equation}
where $\ip{\psi}{0}=0$ or $\ip{\psi}{\ps}=0$.
\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\likely$. 
\end{enumerate}
It is straightforward but tedious to check that $\bar{\mu}$ is a
quantum interval-valued probability measure, and $\bar{\mu}$ is convex
by theorem~\ref{thm:convex-3}. The following argument establishes
that is has an empty core. Assume there is a real-valued probability
measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$ for all $P\in\events$.
Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
we must have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
\begin{equation}
\mu_{\ket{2}}^{B}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
\end{equation}
This measure however is ``better'' than the previous one in the
sense that it might only be induced by $\ket{2}$ or the density matrix
$\mathbb{1}/3$, but not by $\ket{1}$. \end{example}

>>>>

\begin{example}[Three-dimensional quantum three-interval-valued probability
measure]\label{ex:three-dimensional-three-value} Given a three dimensional
Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Let $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $, $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and 
\begin{equation}\eqalign{ 
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})=\imposs\textrm{ ,}\\ 
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\textrm{ ,}\\ 
\bar{\mu}(P) = \unknown\qquad\textrm{otherwise.} 
}\end{equation}
It is straightforward to verify that $\bar{\mu}$ is a quantum interval-valued
probability measure by theorem~\ref{thm:interval-valued-frame-function}
and convex by theorem~\ref{thm:convex-3}. Now assume there exists
a real-valued quantum probability measure $\mu$ such that $\mu(P)\in\bar{\mu}(P)$
for every event (projection)~$P$. We derive a contradiction as follows.
Suppose $\mu(P)\in\bar{\mu}(P)$ then we must have $\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0$.
By Gleason's theorem, there is a mixed state~$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$
such that $\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. However, no pure state~$\ket{\phi}$
can satisfy $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$; a contradiction.
\end{example}

@@

\begin{thm}\label{thm:interval-valued-frame-function}An interval-valued
frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$ satisfies
the following properties:
\begin{itemize}
\item $\bar{f}\left(\lambda\ket{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
for any $\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$. 
\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$,
we have $\left[1,1\right]-\bar{f}\left(\ket{\psi_{i}}\right)\subseteq\bar{f}\left(\ket{\psi_{j}}\right)+\bar{f}\left(\ket{\psi_{k}}\right)$,
where $i$, $j$, and $k$ are any permutations among $0$, $1$,
and $2$. 
\end{itemize}
Conversely, if a function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the above properties, $\bar{f}$ must be an interval-valued
frame function.\end{thm}

\begin{proof} Given a quantum IVPM~$\bar{\mu}$, it is straightforward
to verify that its interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the above properties.

Conversely, given a function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfying the above properties, consider $\bar{\mu}:\events\rightarrow\mathscr{I}$
defined by 
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$ and $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
\item For any $\ket{\psi}\in\mathbb{C}S^{2}$, we have $\bar{\mu}\left(\proj{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
and $\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\left[1,1\right]-\bar{f}\left(\ket{\psi}\right)$. 
\end{itemize}
Since other conditions are trivial, we only need to verify equation~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
First notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
implies equation~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
by induction. Second, equation~(\ref{eq:QuantumInterval-valuedProbability-Complement})
implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(\mathbb{1}-P\right)$.
Therefore, to prove equation~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
it is sufficient to check 
\begin{equation}
\bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)
\end{equation}
for orthogonal $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$. This equation
always holds because the properties of $\bar{f}$.\end{proof}
\begin{definition}For $\ket{\psi}=\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}=\left(\begin{array}{c}\alpha_{0}\\
\alpha_{1}\\
\alpha_{2}
\end{array}\right)$ and $\ket{\phi}=\beta_{0}\ket{0}+\beta_{1}\ket{1}+\beta_{2}\ket{2}=\left(\begin{array}{c}\beta_{0}\\
\beta_{1}\\
\beta_{2}
\end{array}\right)$, their cross product is defined as follow: 
\begin{equation}
\ket{\psi\times\phi}=\ket{\psi}\times\ket{\phi}=\left|\begin{array}{cc}\alpha_{1}^{*} & \beta_{1}^{*}\\
\alpha_{2}^{*} & \beta_{2}^{*}
\end{array}\right|\ket{0}+\left|\begin{array}{cc}\alpha_{2}^{*} & \beta_{2}^{*}\\
\alpha_{0}^{*} & \beta_{0}^{*}
\end{array}\right|\ket{1}+\left|\begin{array}{cc}\alpha_{0}^{*} & \beta_{0}^{*}\\
\alpha_{1}^{*} & \beta_{1}^{*}
\end{array}\right|\ket{2}\textrm{ ,}
\end{equation}
where $\left|\begin{array}{cc}\alpha & \beta\\
\alpha' & \beta'
\end{array}\right|=\alpha\beta'-\alpha'\beta$. Also, even if $\ket{\psi}$ and $\ket{\phi}$ are normalized, their
cross product~$\ket{\psi}\times\ket{\phi}$ need not be normalized
as usual. We will use $\ket{\psi}\times\ket{\phi}$ and
$\ket{\psi}\times\ket{\phi}/\left\Vert
\ket{\psi}\times\ket{\phi}\right\Vert$ interchanged when there is no
confusion.\end{definition}

@@

In order to simplify the discussion, we call a function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$
satisfying conditions in theorem~\ref{thm:interval-valued-frame-function}
a real interval-valued frame function. Obviously, any results in appendix~\ref{sec:Interval-valued-Frame-Functions}
still hold if we replace every ``complex'' by ``real,'' in particular,
replace every $\mathbb{C}S^{2}$ by $S^{2}$. Furthermore, since restricting
the domain of a complex interval-valued frame function to $S^{2}$
gives a real interval-valued frame function, if we prove there is
no real interval-valued frame function satisfying a condition, then
there must be no complex interval-valued frame function satisfying
the corresponding condition. From now on, when we write an interval-valued
frame function~$\bar{f}$ without other specification, we would always
means a real interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$.

@@

\begin{lemma}\label{lemma:imposs-imply-same-value}Given $\theta_{0}\in\left[0,\pi / 2\right]$
and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
then there is $l_{0}\in\left[0,\frac{1}{2}\right]$ such that $\bar{f}\left(\ket{\psi_{0}}\right)=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$
for any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\pi / 2-\theta_{0},\pi / 2\right]\right)$.\end{lemma}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{figureb1.eps} 
\par\end{centering}
\caption{\label{fig:three-dimensional-real-frame-1}This figure is used in
the proof of lemma~\ref{lemma:imposs-imply-same-value}.}
\end{figure}
\begin{proof} We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-1}.
Let the yellow circle is the states whose latitude is $\theta_{0}$.
Then, every states above the yellow circle maps to $\imposs$ by $\bar{f}$.
In particular, $\bar{f}\left(\ket{0}\right)=\bar{f}\left(\ket{0'}\right)=\imposs$.
Since $\left\{ \ket{0'},\ket{1},\ket{2'}\right\} $ is an orthonormal
basis, by theorem~\ref{thm:interval-valued-frame-function}, we have

\begin{equation} 
\eqalign{\left[1,1\right]-\bar{f}\left(\ket{1}\right)\subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{2}\right)=\bar{f}\left(\ket{2'}\right)\\ 
\left[1,1\right]-\bar{f}\left(\ket{2'}\right)\subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{1}\right) 
} 
\label{eq:includes} 
\end{equation}
so that $\bar{f}\left(\ket{2'}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)$.
By the same reason, for any state~$\ket{\psi}$ in the dotted black
circle between $\ket{2'}$ and $\ket{2}$, we have $\bar{f}\left(\ket{\psi}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{2'}\right)$.
Since the angle between $\ket{0}$ and $\ket{0'}$ is the same as
the angle between $\ket{2}$ and $\ket{2'}$, for any $\ket{\psi_{0}}$
and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are in the same longitude,
then $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)$.

@@

Since $\left\{ \ket{A},\ket{B},\ket{C}\right\} $ is an orthonormal
basis and $\bar{f}\left(\ket{A}\right)=\bar{f}\left(\ket{B}\right)=\bar{f}\left(\ket{C}\right)=\left[l_{0},1-l_{0}\right]$,
we have the following inequalities by theorem~\ref{thm:interval-valued-frame-function},
\begin{equation}
\left[1,1\right]-\left[l_{0},1-l_{0}\right]\subseteq\left[2l_{0},2-2l_{0}\right]\Rightarrow l_{0}\le0\textrm{ .}
\end{equation}
Recall that $0\le l_{0}\le\frac{1}{2}$. Therefore, $l_{0}=0$, that
is, $\unknown=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$. \end{proof}

@@

\begin{example}[Three-dimensional quantum 5-interval-valued probability
measure]\label{ex:three-dimensional-5-value} Given a three dimensional
Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Let\emph{ }$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\minus}=\left(\ket{0}-\ket{1}\right)/\sqrt{2}$,
and $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess,\midd\right\} $,
where $\midd$ represents $\left[\frac{1}{4},\frac{3}{4}\right]$.
The definition of $\bar{\mu}$ below refers to figure~\ref{fig:three-dimensional-5-value}
which plots the 1-dimensional projectors: 
\begin{enumerate}
\item Let: 
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs\textrm{ ,}\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\necess\textrm{ ,} 
where $\ket{0}$ and $\ket{\ps}$ are plotted as the red and green
dotted vectors, respectively. 
\item The red and green circles are are the states orthogonal to $\ket{0}$
and $\ket{\ps}$, respectively. We define $\bar{\mu}\left(\proj{\psi}\right)=\bar{\mu}\left(\mathbb{1}-\proj{\psi}\right)=\midd$,
where $\ip{\psi}{0}=0$ or $\ip{\psi}{\ps}=0$.
\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\likely$. 
\end{enumerate}
By theorem~\ref{thm:interval-valued-frame-function}, to check $\bar{\mu}$
a quantum interval-valued probability measure is equivalent to check
$\bar{f}$ satisfying 
\left[1,1\right]-\bar{f}\left(\ket{\psi_0}\right)\subseteq\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\textrm{ ,}\\
\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)\subseteq\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{\psi_0}\right)\textrm{ ,}\\
\left[1,1\right]-\bar{f}\left(\ket{\psi_2}\right)\subseteq\bar{f}\left(\ket{\psi_0}\right)+\bar{f}\left(\ket{\psi_1}\right)\textrm{ ,}
}\label{eq:non-additive-vectors}\end{equation}
for every orthonormal basis~$\mathcal{B}=\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $
where $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}\left(\proj{\psi}\right)$.
We are going to enumerate all possible orthonormal bases to verify
equation~(\ref{eq:non-additive-vectors}), and case 1 and 2 are illustrated
in figure~\ref{fig:three-dimensional-5-value}.
\begin{enumerate}
\item When $\ket{\psi_{0}}$ is $\ket{0}$, then $\ip{\psi_{1}}{0}=\ip{\psi_{2}}{0}=0$.
Equation~(\ref{eq:non-additive-vectors}) can then be verified as
follow. 
\left[1,1\right]-\bar{f}\left(\ket{0}\right)=\necess\subseteq\midd+\midd=\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\textrm{ ,}\\
\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)=\midd\subseteq\midd+\imposs=\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{0}\right)\textrm{ ,}
Similarly, when $\ket{\psi_{0}}$ is $\ket{\ps}$, equation~(\ref{eq:non-additive-vectors})
holds. 
\item When $\ket{0}\notin\mathcal{B}$, $\ket{\ps}\notin\mathcal{B}$, $\ip{\psi_{0}}{0}=0$,
and $\ip{\psi_{1}}{\ps}=0$, we have $\ip{\psi_{2}}{0}\ne0$ and $\ip{\psi_{2}}{\ps}\ne0$.
Then, we have 
\left[1,1\right]-\bar{f}\left(\ket{\psi_0}\right)=\midd\subseteq\midd+\unlikely=\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\textrm{ ,}\\
\left[1,1\right]-\bar{f}\left(\ket{\psi_2}\right)=\likely\subseteq\midd+\midd=\bar{f}\left(\ket{\psi_0}\right)+\bar{f}\left(\ket{\psi_1}\right)\textrm{ .}
\item When $\ket{0}\notin\mathcal{B}$, $\ket{\ps}\notin\mathcal{B}$, $\ip{\psi_{0}}{0}=0$,
$\ip{\psi_{1}}{0}\ne0$, $\ip{\psi_{1}}{\ps}\ne0$, $\ip{\psi_{2}}{0}\ne0$
and $\ip{\psi_{2}}{\ps}\ne0$. Then, we have 
\left[1,1\right]-\bar{f}\left(\ket{\psi_0}\right)=\midd\subseteq\unlikely+\unlikely=\bar{f}\left(\ket{\psi_1}\right)+\bar{f}\left(\ket{\psi_2}\right)\textrm{ ,}\\
\left[1,1\right]-\bar{f}\left(\ket{\psi_1}\right)=\likely\nsubseteq\unlikely+\midd=\bar{f}\left(\ket{\psi_2}\right)+\bar{f}\left(\ket{\psi_0}\right)\textrm{ .}
\footnote{\yutsung{{My previous footnote was wrong. }Need to recompute. Sigh...}}
\item The ``otherwise'' case. Then, equation~(\ref{eq:non-additive-vectors})
can easily be verified. 
\left[1,1\right]-\bar{f}\left(\ket{\psi_{0}}\right)=\likely\subseteq\unlikely+\unlikely=\bar{f}\left(\ket{\psi_{1}}\right)+\bar{f}\left(\ket{\psi_{2}}\right)\textrm{ .}
\end{enumerate}
$\bar{\mu}$ is convex by theorem~\ref{thm:convex-3}. The following
argument establishes that is has an empty core. Assume there is a
real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$
for all $P\in\events$. Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
we must have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
\mu_{\ket{2}}^{B}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
This measure however is ``better'' than the previous one in the
sense that it might only be induced by $\ket{2}$ or the density matrix
$\mathbb{1}/3$, but not by $\ket{1}$. \end{example}
